Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-09 paper/BayesianLISTA.tex
changed mnist to nonnormlized

Figure \ref{fig:mnist_250} presents \textsc{nmse} loss on the validation set with dictionary of size $250$.

@@

%\begin{figure}[t]
%%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
%%~
%\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
%\newline
%%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
%%~
%\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
%\caption{\textsc{mnist} with dictionary $100$}
%\label{fig:mnist_100}
%\end{figure}

>>>>

Figures \ref{fig:mnist_100} and \ref{fig:mnist_250} present quality on the validation set with dictionaries of size $100$ and $250$.

@@

\begin{figure}[t]
%\subfloat[\textsc{nmse} on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_nmse_train}}
%~
\subfloat[\textsc{nmse} on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_nmse_valid}}
\newline
%\subfloat[F measure on train]{\includegraphics[width=0.5\columnwidth]{graphics/mnist/100_normalised_f_measure_train}}
%~
\subfloat[F measure on validation]{\includegraphics[width=\columnwidth]{graphics/mnist/100_normalised_f_measure_valid}}
\caption{\textsc{mnist} with dictionary $100$}
\label{fig:mnist_100}
\end{figure}
